### 2012-08-02 paper/chemokine_main.tex
small edits

A key determinant in the efficiency of chemokine-directed T cell migration towards virus-secreting epithelial cells is the communication distance, defined by the threshold of sufficient chemokine signal to induce directed motion of the cell up the chemical gradient \cite{Thelen2008}.  The diameter of this cloud generated by a single cell is a function of production rate, decay rate, protein diffusion and the sensitivity threshold.  For the threshold of 100 pg/mL and maximal levels of concentration in tissue of 10,000 pg/mL, we calculated the effective communication distance as approximately 250 microns in our model.  This calculation matches the distance calculated for generic cytokines secreted by a suspended solitary cell \cite{Francis1997}.

>>>>

A key determinant in the efficiency of chemokine-directed T cell migration towards virus-secreting epithelial cells is the communication distance, defined by the threshold of sufficient chemokine signal to induce directed motion of the cell up the chemical gradient \cite{Thelen2008}.  The diameter of this cloud generated by a single cell is a function of production rate, decay rate, protein diffusion and the sensitivity threshold.  For the threshold of 10 pg/mL and maximal levels of concentration in tissue of 10,000 pg/mL, we calculated the effective communication distance as approximately 250 microns in our model.  This calculation matches the distance calculated for generic cytokines secreted by a suspended solitary cell \cite{Francis1997}.

### 2012-08-02 paper/chemokine_supplement.tex
small edits

>>>>

\subsection*{Caveats and Limitations}

In both H1N1 strains, the simulated T-cell response fails to clear the infection by day 10.  In the case of pandemic H1N1, the infection rebounds after initial clearance.  We suggest that this is due to the absence of several innate immune agents that were not included in the model.  By removing most of the innate response we were able to focus on the relative effects of the cytokine signaling and T-cell response.  Although H1N1 infections do not clear by day 10, the models show clear differences in capability of managing influenza strains of varying replication rates.  In this model, viral production rate is a major factor in the strength of the infection.

Our model combines the dynamics of human epithelial tissue with the scaling of a mouse's immune system.  We choose to use mouse scale models because ofcomputational limitations.  In our murine-based model the number of cells remained below 100,000, allowing a single model to be run in less than a day.  A human-sized model would be computationally intractable at our level of specificity with current technology.  We use known scaling principals between mice and humans to account for the differences in size \cite{Banerjee2010b}.

In our model T-cell motion depends on the T-cells' sensitivity to chemokine.  Once a T-cell encounters a chemokine concentration above the sensitivity threshold it climbs the chemotactic gradient to the local maxima.  Studies of T-cell chemotaxis show that T-cell movement depends more on the magnitude of the chemokine gradient rather than the concentration \cite{Gao2003}.  Furthermore, T-cells will perform a biased random walk rather than moving in a straight line directly up the concentration gradient [REF].  Biased random walks showed no change in model results, thus we limit T-cell movement to direct motion along the gradient for simplicity.
